### 2020-11-02 Analysis/Code/Sorokin_JMP_2020.Rmd
Proofreading

 abstract: |
  \onehalfspacing \noindent 
  This paper documents that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com). I find that firms close to going one tier up are 4-9% more likely to discount. Two effects could be at play. First, a selection effect arises because customers who buy during a discount could be different from the regular ones, and could potentially leave more positive reviews. Second, a variance effect reflects the idea that positive reviews could help the firm move up a review tier, while negative reviews would keep the tier unchanged, minimizing the downside risk of giving a discount. In order to understand the relative contributions of these effects, I estimate a tractable structural model of demand and reviewing behavior. I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with preferring less variance. I also find that consumers are significantly more likely to leave reviews during a discount. The average selection effect turns out to be small. Additional findings include developing a new approach to estimating demand from data on product usage, estimates of the causal effect of reviews on sales and equilibrium discount elasticities in an important market not previously studied. 
  \thispagestyle{empty}

@@

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfyingly without guidance. Such guidance is now routinely provided by different types of recommendation systems. Many marketplaces or third-party websites allow consumers to review products or services they purchase and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 1 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are important, if not crucial, for a business's success. Not surprisingly, firms take an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors. In this paper I study a novel form of review management: I show that firms can use discounting to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. My question is: would it be profitable for such a product to run a price promotion?

With the help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good during a discount are likely to be different from those who pay the full price and could leave different reviews. If reviews left during a discount tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier. However, these new customers could also prove to be a worse match with the product and leave less favorable reviews. Thus, the sign of the selection effect is ultimately an empirical question. Previous work studying the selection effect in digital markets produced mixed findings. Some of the papers that documented a negative selection effect struggle to explain why firms run promotions which are unlikely to be profitable and are unlikely to attract positive reviews (see the Literature Review section). My variance effect provides a new and attractive explanation for this phenomenon.

The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Additional positive reviews can catapult it to the next review bin, which promises higher sales. In contrast, a few negative reviews might not affect its review tier---and, therefore, sales---by much. Thus, even if the expected effect of price promotion on the reviews is negative, the *expected payoff* could still be positive due to the asymmetry that arises from the tier system's discreteness. Similarly, while extra variance is beneficial for products on the verge of a tier upgrade, it could be harmful to products close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay a price promotion, unless the selection effect is positive and strong.

To quantify these effects, I analyze data from Steam, a major marketplace for computer video games. I build and estimate a structural model of demand and reviewing behavior on this platform. My model admits full heterogeneity between products in the engagement of users and the absolute effects of reviews and discounts on sales. Despite this richness, I show how the parameters, including nonparametric distributions of the random effects, could be estimated. I use this model to lay the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam. Compared to a mediocre review tier, the best tier comes with a premium of as high as 10% in additional sales, and the worst one entails a 13% reduction in sales. My estimates also highlight how impactful discounts are in this market, with an average discount accompanied by a 38% spike in sales. Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given their differential contribution to sales.

I further document that these incentives translate into action. I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability of selling at a discount by up to 4%. I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns. To that end, I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that selection is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level and control for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification that does not control for the selection effect. This finding is consistent with the idea that such products are averse to variance in their review scores. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which discounts create “variance”.

My paper makes an important step towards a bigger goal of studying the life cycles of products in online marketplaces. The flip side of my finding that a product is more likely to be sold at a discount when a review tier transition is close is that it is less likely to run a price promotion when such transition is far. This idea would be a natural input into a model of pricing behavior of a product that maximizes its success over the entire life span. Such a model would exhibit a complicated joint dynamics of review, sales, and price processes. A period of aggressive discounting would help a new product attract customers and transition to the best review tier it can, and would then be followed by a period of high prices that exploit the accumulated reputation. This study serves as a laboratory that isolates some of the effects present in such a model and foreshadows some of the findings and issues that could emerge from it.

I also contribute to the ongoing research effort to improve the design of  recommendation systems. Theoretical advancements have been recently made in understanding separate components of the ideal system, such as exploration of new products vs. exploitation of the established options [@cheHorner18], creation of incentives for firms to invest in quality [@AperjisJohari10], promotion of competition, and reduction of barriers to entry [@Vellodi20]---to name just a few topics and contributions. At the heart of every such inquiry lies a particular strategic interaction between firms, users, and the platform. My paper provides empirical evidence on what some of these interactions result in. I show that firms respond to the tier structure of review systems by changing their pricing behavior around the thresholds and that they use pricing to affect their review process. My estimates can inform future work that will synthesize theoretical and data-driven insights to make concrete design recommendations. For example, @Vellodi20 shows that entry barriers resulting from the low speed of review accumulation by new firms call for a review system that censors the reviews of the most established products. However, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished. My paper directly informs this design question by quantifying two fundamental forces involved: the frequency with which firms change prices to influence their review status and the response of the reviewing behavior to these changes in prices.

@@

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on product outcomes. To my knowledge, it was the first paper to use Steam to study the causal effect of online reviews. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a new way: by formulating a structural model of the data generating process. With the help of this model, I manage to extract information on product sales from usage data. I compare the structural model estimates with the ones obtained by its simpler regression analog and find important similarities and dissimilarities. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

With the benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways for firms to affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors and good reviews for themselves. @LucaZervas16 provides similar evidence for restaurants on Yelp. A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives. @GuYe14 provides evidence that consumers who had once left a negative review of their hotel experience were more likely to leave a positive review for the same hotel in the future if their first review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage unfavorable review activity. The idea is that consumers receive a signal that the firm is “listening” to them and are stimulated to leave negative reviews that they deem more influential.

However, direct ways of managing online reputation discussed above are not the only avenues through which businesses can affect their reviews. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by promotion are different from regular customers and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion. @Li16 confirms the finding in the same market but finds that restaurants with fewer and worse reviews can benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative reviews. In an experimental study on eBay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback. The effect is explained by clients reciprocating to the rebate, and not by the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow discounts instead of studying the continuous effect of a price promotion on the review score.

Based on its findings, @ByersEtAl12 cautions restaurants to treat Groupon customers well to avoid adverse effects on online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, finding a negative selection effect in the data presents a puzzle\footnote{Direct profitability of Groupon promotions is questionable; see \citet{Dholakia11}.}. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free to build a reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which undermines the strategy. I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it will find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial. My variance effect conceptually echoes the “Gambling for Resurrection” effect from the political science and finance literatures [@DownsRocke94]. If this type of reasoning is commonplace among firms, then the researcher would observe free pricing to deteriorate review scores, on average, even if the average effect on sales remains positive.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in that section contributes greatly to its size, but the purpose is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales and showing that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of a discounting decision for a product close to a review tier transition and introduces the selection and the variance effects. The section proceeds by studying such decisions in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity and estimates its parameters to quantify the relative contributions of the selection and the variance effects to observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it  earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD, Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to stuy in its own right.

Any user who owns a game on Steam can leave a review for that game. Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). Steam is, thus, different from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge]. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review tiers* to each game. These labels\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its price or if the game is currently sold at a discount.

Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an homage to the masterfully chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative” have a very similar contribution to visibility on the platform, which implies, among other things, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database contains time series of prices and player activity for each game on Steam on a daily level. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent players for each game on a daily basis. To clarify this definition, consider an example game that, on some day, was played by 10 people at every hour, except noon, when 13 people played the game simultaneously. The recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.

@@

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam has made some significant changes to its review system in late 2016, and one of the effects was the removal of a big number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period make it to the sample.

>>>>

 abstract: |
  \onehalfspacing \noindent 
  This paper documents that firms in online marketplaces use price promotions to facilitate transitions to better review tiers (similar to the number of stars on Amazon.com). I find that firms close to upgrading their tier are 4-9% more likely to discount. Two effects could be at play. First, a selection effect arises because customers who buy during a discount could be different from the regular ones, and could potentially leave more positive reviews. Second, a variance effect reflects the idea that positive reviews could help the firm move up a review tier, while negative reviews would keep the tier unchanged, minimizing the downside risk of giving a discount. In order to understand the relative contributions of these effects, I estimate a tractable structural model of demand and reviewing behavior. I find evidence of the importance of the variance effect: when the selection effect is controlled for, firms close to downgrading their review tier are 6% less likely to give a discount, consistent with them preferring less variance. I also find that consumers are significantly more likely to leave reviews during a discount. The average selection effect turns out to be small. Additional findings include the development of a new approach to estimating demand from data on product usage, estimates of the causal effect of reviews on sales, and equilibrium discount elasticities in an important market that has not been previously studied. 
  \thispagestyle{empty}

@@

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfyingly without guidance. Such guidance is now routinely provided by different types of recommendation systems. Many marketplaces or third-party websites allow consumers to review products or services they purchase and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 1 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both extensive literature in marketing and anecdotal evidence from these markets suggest that good reviews are important, if not crucial, for a business's success. Not surprisingly, firms take an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors. In this paper I study a novel form of review management: I show that firms can use discounting to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. My question is: would it be profitable for such a product to run a price promotion?

With the help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good during a discount are likely to be different from those who pay the full price and could leave different reviews. If reviews left during a discount tend to be more favorable, then the induced positive selection effect creates an incentive for the product to go on sale, as new customers are likely to leave positive reviews and help the product advance to the next review tier. However, these new customers could also prove to be a worse match with the product and leave less favorable reviews. Therefore, the sign of the selection effect is ultimately an empirical question. Previous work studying the selection effect in digital markets has produced mixed findings. Some of the papers that documented a negative selection effect struggle to explain why firms run promotions which are unlikely to be profitable and are unlikely to attract positive reviews (see the Literature Review section). My variance effect provides a new and attractive explanation for this phenomenon.

The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Additional positive reviews can propel it to the next review bin, which promises higher sales. In contrast, a few negative reviews might not affect its review tier---and, therefore, sales---by much. Thus, even if the expected effect of price promotion on the reviews is negative, the *expected payoff* could still be positive due to the asymmetry that arises from the tier system's discreteness. Similarly, while extra variance is beneficial for products on the verge of a tier upgrade, it could be harmful to products close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay a price promotion, unless the selection effect is positive and strong.

To quantify these effects, I analyze data from Steam, a major marketplace for computer video games. I build and estimate a structural model of demand and reviewing behavior on this platform. My model admits full heterogeneity between products in the engagement of users and the absolute effects of reviews and discounts on sales. Despite this richness, I show how the parameters, including nonparametric distributions of the random effects, could be estimated. I use this model to lay the groundwork for my analysis, as it helps me confirm the importance of better review tiers for sales on Steam. Compared to a mediocre review tier, the best tier comes with a premium of as high as 10% in additional sales, while the worst tier entails a 13% reduction in sales. My estimates also highlight how impactful discounts are in this market, with an average discount accompanied by a 38% spike in sales. Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given their differential contribution to sales.

I further document that these incentives translate into action. I find that products that are close to upgrading their review tier are 4-9% more likely to sell at a discount, and I find some evidence that proximity to a downward transition decreases the probability of selling at a discount by up to 4%. I then employ my structural model to disentangle the relative contributions of the variance and the selection effects to the observed discounting patterns. To that end, I estimate the effect of discounts on the probability of a product receiving a positive or a negative review. I find no evidence that selection is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level and control for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products close to a review downgrade are 6% less likely to discount---an increase in both the size and the significance of the effect compared to the specification which does not control for the selection effect. This finding is consistent with the idea that such products are averse to variance in their review scores. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which discounts create “variance.”

My paper makes an important step towards a bigger goal of studying the life cycles of products in online marketplaces. The flip side of my finding that a product is more likely to be sold at a discount when a review tier transition is close is that it is less likely to run a price promotion when such transition is far. This idea would be a natural input into a model of pricing behavior of a product that maximizes its success over the entire life span. Such a model would exhibit a complicated joint dynamics of review, sales, and price processes. A period of aggressive discounting would help a new product attract customers and transition to the best review tier attainable, and would then be followed by a period of high prices that exploit the accumulated stock of reviews. This study serves as a laboratory that isolates some of the effects present in such a model and foreshadows some of the findings and issues that could emerge from it.

I also contribute to the ongoing research effort to improve the design of  recommendation systems. Theoretical advancements have been recently made in understanding separate components of the ideal system, such as exploration of new products vs. exploitation of the established options [@cheHorner18], creation of incentives for firms to invest in quality [@AperjisJohari10], promotion of competition, and reduction of barriers to entry [@Vellodi20], to name just a few topics and contributions. At the heart of every such inquiry lies a particular strategic interaction between firms, users, and the platform. My paper provides empirical evidence on the results of some of these interactions. I show that firms respond to the tier structure of review systems by changing their pricing behavior around the review tier thresholds and that they use pricing to affect their review process. My estimates can inform future work that will synthesize theoretical and data-driven insights to make concrete design recommendations. For example, @Vellodi20 shows that entry barriers resulting from the low speed of review accumulation by new firms necessitate a review system that censors the reviews of the most established products. However, when firms can offer lower prices to build up the crucial review base, the need for the design intervention is diminished. My paper directly informs this design question by quantifying two fundamental forces involved: the frequency with which firms change prices to influence their review status and the response of the reviewing behavior to these changes in prices.

@@

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on product outcomes. To my knowledge, it was the first paper to use Steam to study the causal effect of online reviews. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data. I use the data from that paper, but confront the absence of sales data in a new way: I formulate a structural model of the data generating process. With the help of this model, I manage to extract information on product sales from usage data. I compare the structural model estimates with the ones obtained by its simpler regression analog and find important similarities and dissimilarities. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

With the benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways for firms to affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors and good reviews for themselves. @LucaZervas16 provides similar evidence for restaurants on Yelp. A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives. @GuYe14 provides evidence that consumers who had once left a negative review of their hotel experience were more likely to leave a positive review for the same hotel in the future if their first review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the sentiment and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they may receive a response. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage unfavorable review activity. The idea is that consumers receive a signal that the firm is “listening” to them and are stimulated to leave negative reviews that they deem more influential.

However, direct ways of managing online reputation discussed above are not the only avenues through which businesses can affect their reviews. Another strand of literature is concerned with whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers---and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. Worse match quality between the restaurants and the exploring Groupon customers could explain the dip in the review score following a price promotion. @Li16 confirms the finding in the same market but finds that restaurants with fewer and worse reviews can benefit from participating in a Groupon promotion. There are a few other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative reviews. In an experimental study on eBay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback. The effect is explained by clients reciprocating to the rebate, and not by the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow discounts instead of studying the continuous effect of a price promotion on the review score.

Based on its findings, @ByersEtAl12 cautions restaurants to treat Groupon customers well to avoid adverse effects on online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, finding a negative selection effect in the data presents a puzzle\footnote{Direct profitability of Groupon promotions is questionable; see \citet{Dholakia11}.}. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free to build a reputation and escape the "zero reviews trap." While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which undermines the strategy. I provide a novel mechanism---the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it will find it profitable to sell for free even if the probability of soliciting favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial. My variance effect conceptually echoes the “Gambling for Resurrection” effect from the political science and finance literatures [@DownsRocke94]. If this type of reasoning is commonplace among firms, then the researcher would observe free pricing to deteriorate review scores, on average, even if the average effect on sales remains positive.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in that section contributes greatly to its size, but the purpose is to simply lay the groundwork for the main analysis by quantifying the importance of different review tiers on sales and showing that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of a discounting decision for a product close to a review tier transition and introduces the selection and the variance effects. The section proceeds by studying such decisions in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} with a model of reviewing activity and estimates its parameters to quantify the relative contributions of the selection and the variance effects to observed patterns of discounting around review transitions. Section \ref{conclusion} concludes the paper.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it  earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given the ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD, Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to study in its own right.

Any user who owns a game on Steam can leave a review for that game. Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). Steam is, thus, different from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This lends me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge]. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave ethically.

A review consists of a binary grade, "thumbs up" or "thumbs down," and text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review tiers* to each game. These labels\footnote{I use the words “tier”, “bin”, and “label” interchangebly througout the text} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”}. For example, a game with 7 positive and 2 negative reviews would not have a review score nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games. This selection could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its price or if the game is currently sold at a discount.

Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why I choose to focus on the review labels as my main explanatory review variables later in the analysis, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an homage to the masterfully chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will attract more customers and have higher sales, other things equal. Crucially, according to Steam's documentation, all review labels better than “Negative” have a very similar contribution to visibility on the platform, which implies, among other things, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. However, Steam Database also contains time series of prices and player activity for each game on Steam on a daily level. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly provide such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent players for each game on a daily basis. To clarify this definition, consider an example game that, on some day, was played by 10 people at every hour, except noon, when 13 people played the game simultaneously. The recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.

@@

Steam is home to more than 25,000 games that differ in their genres, prices, sales, release dates, frequency of updates, and other characteristics. Inevitably, an appropriate sample should be selected for the analysis. @SorokinStevens20 studies the causal effect of reviews on sales on Steam, and I mirror closely the sample selection procedure used in that paper. First, Steam made some significant changes to its review system in late 2016, and one of the effects was the removal of a large number of reviews from the review score calculation. While it could be an intervention that is worthy of an independent study, in practice combining the data from before and after the intervention led to unsound results, so I focus on the two year period from January 2017 to January 2019, keeping the review system as stable as possible. In particular, only games that were released in this time period are included in the sample.
